# Conclusion

The goal for this project was to perform statistical analysis on the sea turtle nest locations and determine if there is a statistically significant difference between these nest locations and the others. 

## Summary: Interpretation

This analysis determined that statistically significant differences between the nest line and other locations exist. Foreshore slope differences exist between the nest line and 25E, 50E, 100E, and 100W, as well as between 50E and 50W. Beach Slope differences exist between the nest line and 25E, 25W, 50E, 50W, and 100W, as well as between 100W and 100E. Beach width differences exist between the nest line and 25W and 25E. No significant differences in foredune height were found between any variables.

## Limitations

There were limitations for the project that may have affected results. The data was collected only on Pensacola Beach, which may or may not apply to other locations. The data also consisted of fourteen loggerhead turtle nests and one green turtle nest, which is an uneven balance of species.  Inference cannot be made on green turtles due to the lack of sample size and thus, was excluded from analysis. Fifteen is also a relatively small sample size. A larger sample size will provide more accurate estimation, tighter confidence intervals, and the ability to perform more complex statistical analysis, such as modeling using regression analysis. Finally, this data only examines sea turtle nesting behavior for a single year; longitudinal data should be collected for a more complete picture of sea turtle preferences.

# References {-}

1. Cuevas E, Liceaga-Correa M, & Marino-Tapia I. (2010). Influence of Beach Slope and Width on Hawksbill (Eretmochelys imbricata) and Green Turtle (Chelonia mydas) Nesting Activity in El Cuyo, Yucatan, Mexico. Chelonian Research Foundation. Retrieved from 10.2744/CCB-0819.1

2. Culver M, Gibeaut JC, Shaver DJ, Tissot P, & Starek M (2020). Using Lidar Data to Assess the Relationship Between Beach Geomorphology and Kemp’s Ridley (Lepidochelys kempii) Nest Site Selection Along Padre Island, TX, United States. Front. Mar. Sci. 7:214. Retrieved from https://doi.org/10.3389/fmars.2020.00214

3. Mortimer J. (1990). The Influence of Beach Sand Characteristics on the Nesting Behavior and Clutch Survival of Green Turtles (Chelonia mydas). American Society of Ichthyologists and Herpetologists (ASIH). Retrieved from https://doi.org/10.2307/1446446

4. Provancha J & Ehrhart L. (1987). Sea Turtle Nesting Trends at Kennedy Space Center and Cape Canaveral Air Force Station, Florida, and Relationships with Factors Influencing Nest Site Selection. ResearchGate. Retrieved from https://www.researchgate.net/publication/24320682

5. Zavaleta-Lizarraga L & Morales-Mavil J. (2013). Nest site selection by the green turtle (Chelonia mydas) in a beach of the north of Veracruz, Mexico. ResearchGate. Retrieved from 10.7550/rmb.31913

# Appendix {-}

Below are the QQ plots used to assess normality

```{r}
annotate_figure(mfsn, top = text_grob("Foreshore Slope Difference with Nestline", color = "black", face = "bold", size = 20))

annotate_figure(mbsn, top = text_grob("Beach Slope Difference with Nestline", color = "black", face = "bold", size = 20))

annotate_figure(mfsn, top = text_grob("Beach Width Difference with Nestline", color = "black", face = "bold", size = 20))

annotate_figure(mfsn, top = text_grob("Foredune Height Difference with Nestline", color = "black", face = "bold", size = 20))

annotate_figure(mwe, top = text_grob("All Variables Difference Between E and W", color = "black", face = "bold", size = 20))
```


Below is the entirety of the code used for this project

```{r echo = TRUE, eval=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, eval = FALSE)
library(gsheet)
library(tidyverse)
library(ggpubr)
library(asbio)
library(tidyr)
options(scipen = 999)
#call in data
data <- as_tibble(gsheet2tbl("https://docs.google.com/spreadsheets/d/1IRNiGVwJtBPyLTnl4HaVTo0rfIX90HlRSm7P0EH3_Zs/edit"))


# Boxplots

data$location <- factor(data$location, c("100W", "50W", "25W", "Nestline", "25E", "50E", "100E"))

bp1 <- ggplot(data=data, aes(y= foreshore_slope, x=location, fill=location)) +
          geom_boxplot() +
          theme_minimal() +
          labs(y = "Angle (Degrees)", x = "Location") +
          ylim(min=2.5, max=10) +
          ggtitle("Foreshore Slope Angle")
bp1

bp2 <- ggplot(data=data, aes(y= beach_slope, x=location, fill=location)) +
          geom_boxplot() +
          theme_minimal() +
          labs(y = "Angle (Degrees)", x = "Location") +
          ylim(min=0, max=3) +
          ggtitle("Beach Slope Angle")
bp2

bp3 <- ggplot(data=data, aes(y= beach_width, x=location, fill=location)) +
          geom_boxplot() +
          theme_minimal() +
          labs(y = "Width (M)", x = "Location") +
          ylim(min=20, max=50) +
          ggtitle("Beach Width")
bp3

bp4 <- ggplot(data=data, aes(y= foredune_height, x=location, fill=location)) +
          geom_boxplot() +
          theme_minimal() +
          labs(y = "Height (M)", x = "Location") +
          ylim(min=3, max=6) +
          ggtitle("Foredune Height")
bp4



# Making calculations easy

data_nestline <- data %>% filter(location == "Nestline")
data_25w <- data %>% filter(location == "25W")
data_25e <- data %>% filter(location == "25E")
data_50w <- data %>% filter(location == "50W")
data_50e <- data %>% filter(location == "50E")
data_100w <- data %>% filter(location == "100W")
data_100e <- data %>% filter(location == "100E")


# Generating Differences between Nestline

data_nestline$fsn25w <- data_nestline$foreshore_slope - data_25w$foreshore_slope
data_nestline$fsn25e <- data_nestline$foreshore_slope - data_25e$foreshore_slope
data_nestline$fsn50w <- data_nestline$foreshore_slope - data_50w$foreshore_slope
data_nestline$fsn50e <- data_nestline$foreshore_slope - data_50e$foreshore_slope
data_nestline$fsn100w <- data_nestline$foreshore_slope - data_100w$foreshore_slope
data_nestline$fsn100e <- data_nestline$foreshore_slope - data_100e$foreshore_slope

data_nestline$bsn25w <- data_nestline$beach_slope - data_25w$beach_slope
data_nestline$bsn25e <- data_nestline$beach_slope - data_25e$beach_slope
data_nestline$bsn50w <- data_nestline$beach_slope - data_50w$beach_slope
data_nestline$bsn50e <- data_nestline$beach_slope - data_50e$beach_slope
data_nestline$bsn100w <- data_nestline$beach_slope - data_100w$beach_slope
data_nestline$bsn100e <- data_nestline$beach_slope - data_100e$beach_slope

data_nestline$bwn25w <- data_nestline$beach_width - data_25w$beach_width
data_nestline$bwn25e <- data_nestline$beach_width - data_25e$beach_width
data_nestline$bwn50w <- data_nestline$beach_width - data_50w$beach_width
data_nestline$bwn50e <- data_nestline$beach_width - data_50e$beach_width
data_nestline$bwn100w <- data_nestline$beach_width - data_100w$beach_width
data_nestline$bwn100e <- data_nestline$beach_width - data_100e$beach_width

data_nestline$fhn25w <- data_nestline$foredune_height - data_25w$foredune_height
data_nestline$fhn25e <- data_nestline$foredune_height - data_25e$foredune_height
data_nestline$fhn50w <- data_nestline$foredune_height - data_50w$foredune_height
data_nestline$fhn50e <- data_nestline$foredune_height - data_50e$foredune_height
data_nestline$fhn100w <- data_nestline$foredune_height - data_100w$foredune_height
data_nestline$fhn100e <- data_nestline$foredune_height - data_100e$foredune_height


# Generating differences between E and W

data_nestline$fs25we <- data_25e$foreshore_slope - data_25w$foreshore_slope
data_nestline$fs50we <- data_50e$foreshore_slope - data_50w$foreshore_slope
data_nestline$fs100we <- data_100e$foreshore_slope - data_100w$foreshore_slope

data_nestline$bs25we <- data_25e$beach_slope - data_25w$beach_slope
data_nestline$bs50we <- data_50e$beach_slope - data_50w$beach_slope
data_nestline$bs100we <- data_100e$beach_slope - data_100w$beach_slope

data_nestline$bw25we <- data_25e$beach_width - data_25w$beach_width
data_nestline$bw50we <- data_50e$beach_width - data_50w$beach_width
data_nestline$bw100we <- data_100e$beach_width - data_100w$beach_width

data_nestline$fh25we <- data_25e$foredune_height - data_25w$foredune_height
data_nestline$fh50we <- data_50e$foredune_height - data_50w$foredune_height
data_nestline$fh100we <- data_100e$foredune_height - data_100w$foredune_height



# Wilcoxon Signed-Rank and Confidence Interval

#foreshore slope
wilcox.test(data_nestline$fsn25w, correct = T, exact = F)
ci.median(data_nestline$fsn25w, conf = 0.9)

wilcox.test(data_nestline$fsn25e, correct = T, exact = F)
ci.median(data_nestline$fsn25e, conf = 0.9)

wilcox.test(data_nestline$fsn50w, correct = T, exact = F)
ci.median(data_nestline$fsn50w, conf = 0.9)

wilcox.test(data_nestline$fsn50e, correct = T, exact = F)
ci.median(data_nestline$fsn50e, conf = 0.9)

wilcox.test(data_nestline$fsn100w, correct = T, exact = F)
ci.median(data_nestline$fsn100w, conf = 0.9)

wilcox.test(data_nestline$fsn100e, correct = T, exact = F)
ci.median(data_nestline$fsn100e, conf = 0.9)

#beach slope
wilcox.test(data_nestline$bsn25w, correct = T, exact = F)
ci.median(data_nestline$bsn25w, conf = 0.9)

wilcox.test(data_nestline$bsn25e, correct = T, exact = F)
ci.median(data_nestline$bsn25e, conf = 0.9)

wilcox.test(data_nestline$bsn50w, correct = T, exact = F)
ci.median(data_nestline$bsn50w, conf = 0.9)

wilcox.test(data_nestline$bsn50e, correct = T, exact = F)
ci.median(data_nestline$bsn50e, conf = 0.9)

wilcox.test(data_nestline$bsn100w, correct = T, exact = F)
ci.median(data_nestline$bsn100w, conf = 0.9)

wilcox.test(data_nestline$bsn100e, correct = T, exact = F)
ci.median(data_nestline$bsn100e, conf = 0.9)

#beach width
wilcox.test(data_nestline$bwn25w, correct = T, exact = F)
ci.median(data_nestline$bwn25w, conf = 0.9)

wilcox.test(data_nestline$bwn25e, correct = T, exact = F)
ci.median(data_nestline$bwn25e, conf = 0.9)

wilcox.test(data_nestline$bwn50w, correct = T, exact = F)
ci.median(data_nestline$bwn50w, conf = 0.9)

wilcox.test(data_nestline$bwn50e, correct = T, exact = F)
ci.median(data_nestline$bwn50e, conf = 0.9)

wilcox.test(data_nestline$bwn100w, correct = T, exact = F)
ci.median(data_nestline$bwn100w, conf = 0.9)

wilcox.test(data_nestline$bwn100e, correct = T, exact = F)
ci.median(data_nestline$bwn100e, conf = 0.9)

#foredune height
wilcox.test(data_nestline$fhn25w, correct = T, exact = F)
ci.median(data_nestline$fhn25w, conf = 0.9)

wilcox.test(data_nestline$fhn25e, correct = T, exact = F)
ci.median(data_nestline$fhn25e, conf = 0.9)

wilcox.test(data_nestline$fhn50w, correct = T, exact = F)
ci.median(data_nestline$fhn50w, conf = 0.9)

wilcox.test(data_nestline$fhn50e, correct = T, exact = F)
ci.median(data_nestline$fhn50e, conf = 0.9)

wilcox.test(data_nestline$fhn100w, correct = T, exact = F)
ci.median(data_nestline$fhn100w, conf = 0.9)

wilcox.test(data_nestline$fhn100e, correct = T, exact = F)
ci.median(data_nestline$fhn100e, conf = 0.9)


# East vs West

#foreshore slope
wilcox.test(data_nestline$fs25we, correct = T, exact = F)
ci.median(data_nestline$fs25we, conf = 0.9)

wilcox.test(data_nestline$fs50we, correct = T, exact = F)
ci.median(data_nestline$fs50we, conf = 0.9)

wilcox.test(data_nestline$fs100we, correct = T, exact = F)
ci.median(data_nestline$fs100we, conf = 0.9)

#beach slope
wilcox.test(data_nestline$bs25we, correct = T, exact = F)
ci.median(data_nestline$bs25we, conf = 0.9)

wilcox.test(data_nestline$bs50we, correct = T, exact = F)
ci.median(data_nestline$bs50we, conf = 0.9)

wilcox.test(data_nestline$bs100we, correct = T, exact = F)
ci.median(data_nestline$bs100we, conf = 0.9)

#beach width
wilcox.test(data_nestline$bw25we, correct = T, exact = F)
ci.median(data_nestline$bw25we, conf = 0.9)

wilcox.test(data_nestline$bw50we, correct = T, exact = F)
ci.median(data_nestline$bw50we, conf = 0.9)

wilcox.test(data_nestline$bw100we, correct = T, exact = F)
ci.median(data_nestline$bw100we, conf = 0.9)

#foredune height
wilcox.test(data_nestline$fh25we, correct = T, exact = F)
ci.median(data_nestline$fh25we, conf = 0.9)

wilcox.test(data_nestline$fh50we, correct = T, exact = F)
ci.median(data_nestline$fh50we, conf = 0.9)

wilcox.test(data_nestline$fh100we, correct = T, exact = F)
ci.median(data_nestline$fh100we, conf = 0.9)

# Dot Plots for Differences

#foreshore slope
gfsn25w <- data_nestline %>% ggplot(aes(x = nest, y = fsn25w, color = Species)) +
  geom_point(size = 2) +
  scale_color_manual(values = c("Loggerhead" = "#004C97", "Green" = "#40A829")) +
  xlab("Nest") + 
  ylab("Difference (°)") + 
  ggtitle("25w") +
  ylim(min=-2.5, max=4) +
  theme_minimal()

  gfsn25e <- data_nestline %>% ggplot(aes(x = nest, y = fsn25e, color = Species)) +
  geom_point(size = 2) +
  scale_color_manual(values = c("Loggerhead" = "#004C97", "Green" = "#40A829")) +
  xlab("Nest") + 
  ylab("Difference (°)") + 
  ggtitle("25e") +
  ylim(min=-2.5, max=4) +
  theme_minimal()
  
  gfsn50w <- data_nestline %>% ggplot(aes(x = nest, y = fsn50w, color = Species)) +
  geom_point(size = 2) +
  scale_color_manual(values = c("Loggerhead" = "#004C97", "Green" = "#40A829")) +
  xlab("Nest") + 
  ylab("Difference (°)") + 
  ggtitle("50w") +
  ylim(min=-2.5, max=4) +
  theme_minimal()

  
  gfsn50e <- data_nestline %>% ggplot(aes(x = nest, y = fsn50e, color = Species)) +
  geom_point(size = 2) +
  scale_color_manual(values = c("Loggerhead" = "#004C97", "Green" = "#40A829")) +
  xlab("Nest") + 
  ylab("Difference (°)") + 
  ggtitle("50e") +
  ylim(min=-2.5, max=4) +
  theme_minimal()

  
  gfsn100w <- data_nestline %>% ggplot(aes(x = nest, y = fsn100w, color = Species)) +
  geom_point(size = 2) +
  scale_color_manual(values = c("Loggerhead" = "#004C97", "Green" = "#40A829")) +
  xlab("Nest") + 
  ylab("Difference (°)") + 
  ggtitle("100w") +
  ylim(min=-2.5, max=4) +
  theme_minimal()
  
  gfsn100e <- data_nestline %>% ggplot(aes(x = nest, y = fsn100e, color = Species)) +
  geom_point(size = 2) +
  scale_color_manual(values = c("Loggerhead" = "#004C97", "Green" = "#40A829")) +
  xlab("Nest") + 
  ylab("Difference (°)") + 
  ggtitle("100e") +
  ylim(min=-2.5, max=4) +
  theme_minimal()

#beach slope
  gbsn25w <- data_nestline %>% ggplot(aes(x = nest, y = bsn25w, color = Species)) +
  geom_point(size = 2) +
  scale_color_manual(values = c("Loggerhead" = "#004C97", "Green" = "#40A829")) +
  xlab("Nest") + 
  ylab("Difference (°)") + 
  ggtitle("25w") +
  ylim(min=-2.25, max=2) +
  theme_minimal()

  
  gbsn25e <- data_nestline %>% ggplot(aes(x = nest, y = bsn25e, color = Species)) +
  geom_point(size = 2) +
  scale_color_manual(values = c("Loggerhead" = "#004C97", "Green" = "#40A829")) +
  xlab("Nest") + 
  ylab("Difference (°)") + 
  ggtitle("25e") +
  ylim(min=-2.25, max=2) +
  theme_minimal()

  
  gbsn50w <- data_nestline %>% ggplot(aes(x = nest, y = bsn50w, color = Species)) +
  geom_point(size = 2) +
  scale_color_manual(values = c("Loggerhead" = "#004C97", "Green" = "#40A829")) +
  xlab("Nest") + 
  ylab("Difference (°)") + 
  ggtitle("50w") +
  ylim(min=-2.25, max=2) +
  theme_minimal()
  
  gbsn50e <- data_nestline %>% ggplot(aes(x = nest, y = bsn50e, color = Species)) +
  geom_point(size = 2) +
  scale_color_manual(values = c("Loggerhead" = "#004C97", "Green" = "#40A829")) +
  xlab("Nest") + 
  ylab("Difference (°)") + 
  ggtitle("50e") +
  ylim(min=-2.25, max=2) +
  theme_minimal()
 
  
  gbsn100w <- data_nestline %>% ggplot(aes(x = nest, y = bsn100w, color = Species)) +
  geom_point(size = 2) +
  scale_color_manual(values = c("Loggerhead" = "#004C97", "Green" = "#40A829")) +
  xlab("Nest") + 
  ylab("Difference (°)") + 
  ggtitle("100w") +
  ylim(min=-2.25, max=2) +
  theme_minimal()
 
  
  gbsn100e <- data_nestline %>% ggplot(aes(x = nest, y = bsn100e, color = Species)) +
  geom_point(size = 2) +
  scale_color_manual(values = c("Loggerhead" = "#004C97", "Green" = "#40A829")) +
  xlab("Nest") + 
  ylab("Difference (°)") + 
  ggtitle("100e") +
  ylim(min=-2.25, max=2) +
  theme_minimal()

#beach width
  gbwn25w <- data_nestline %>% ggplot(aes(x = nest, y = bwn25w, color = Species)) +
  geom_point(size = 2) +
  scale_color_manual(values = c("Loggerhead" = "#004C97", "Green" = "#40A829")) +
  xlab("Nest") + 
  ylab("Difference (m)") + 
  ggtitle("25w") +
  ylim(min=-13, max=13) +
  theme_minimal()

  
  gbwn25e <- data_nestline %>% ggplot(aes(x = nest, y = bwn25e, color = Species)) +
  geom_point(size = 2) +
  scale_color_manual(values = c("Loggerhead" = "#004C97", "Green" = "#40A829")) +
  xlab("Nest") + 
  ylab("Difference (m)") + 
  ggtitle("25e") +
  ylim(min=-13, max=13) +
  theme_minimal()

  
  gbwn50w <- data_nestline %>% ggplot(aes(x = nest, y = bwn50w, color = Species)) +
  geom_point(size = 2) +
  scale_color_manual(values = c("Loggerhead" = "#004C97", "Green" = "#40A829")) +
  xlab("Nest") + 
  ylab("Difference (m)") + 
  ggtitle("50w") +
  ylim(min=-13, max=13) +
  theme_minimal()

  
  gbwn50e <- data_nestline %>% ggplot(aes(x = nest, y = bwn50e, color = Species)) +
  geom_point(size = 2) +
  scale_color_manual(values = c("Loggerhead" = "#004C97", "Green" = "#40A829")) +
  xlab("Nest") + 
  ylab("Difference (m)") + 
  ggtitle("50e") +
  ylim(min=-13, max=13) +
  theme_minimal()

  
  gbwn100w <- data_nestline %>% ggplot(aes(x = nest, y = bwn100w, color = Species)) +
  geom_point(size = 2) +
  scale_color_manual(values = c("Loggerhead" = "#004C97", "Green" = "#40A829")) +
  xlab("Nest") + 
  ylab("Difference (m)") + 
  ggtitle("100w") +
  ylim(min=-13, max=13) +
  theme_minimal()

  
  gbwn100e <- data_nestline %>% ggplot(aes(x = nest, y = bwn100e, color = Species)) +
  geom_point(size = 2) +
  scale_color_manual(values = c("Loggerhead" = "#004C97", "Green" = "#40A829")) +
  xlab("Nest") + 
  ylab("Difference (m)") + 
  ggtitle("100e") +
  ylim(min=-13, max=13) +
  theme_minimal()


#foredune height
  gfhn25w <- data_nestline %>% ggplot(aes(x = nest, y = fhn25w, color = Species)) +
  geom_point(size = 2) +
  scale_color_manual(values = c("Loggerhead" = "#004C97", "Green" = "#40A829")) +
  xlab("Nest") + 
  ylab("Difference (m)") + 
  ggtitle("25w") +
  ylim(min=-0.75, max=1.25) +
  theme_minimal()

  
  gfhn25e <- data_nestline %>% ggplot(aes(x = nest, y = fhn25e, color = Species)) +
  geom_point(size = 2) +
  scale_color_manual(values = c("Loggerhead" = "#004C97", "Green" = "#40A829")) +
  xlab("Nest") + 
  ylab("Difference (m)") + 
  ggtitle("25e") +
  ylim(min=-0.75, max=1.25) +
  theme_minimal()
 
  
  gfhn50w <- data_nestline %>% ggplot(aes(x = nest, y = fhn50w, color = Species)) +
  geom_point(size = 2) +
  scale_color_manual(values = c("Loggerhead" = "#004C97", "Green" = "#40A829")) +
  xlab("Nest") + 
  ylab("Difference (m)") + 
  ggtitle("50w") +
  ylim(min=-0.75, max=1.25) +
  theme_minimal()

  
  gfhn50e <- data_nestline %>% ggplot(aes(x = nest, y = fhn50e, color = Species)) +
  geom_point(size = 2) +
  scale_color_manual(values = c("Loggerhead" = "#004C97", "Green" = "#40A829")) +
  xlab("Nest") + 
  ylab("Difference (m)") + 
  ggtitle("50e") +
  ylim(min=-0.75, max=1.25) +
  theme_minimal()
 
  
  gfhn100w <- data_nestline %>% ggplot(aes(x = nest, y = fhn100w, color = Species)) +
  geom_point(size = 2) +
  scale_color_manual(values = c("Loggerhead" = "#004C97", "Green" = "#40A829")) +
  xlab("Nest") + 
  ylab("Difference (m)") + 
  ggtitle("100w") +
  ylim(min=-0.75, max=1.25) +
  theme_minimal()
 
  
  gfhn100e <- data_nestline %>% ggplot(aes(x = nest, y = fhn100e, color = Species)) +
  geom_point(size = 2) +
  scale_color_manual(values = c("Loggerhead" = "#004C97", "Green" = "#40A829")) +
  xlab("Nest") + 
  ylab("Difference (m)") + 
  ggtitle("100e") +
  ylim(min=-0.75, max=1.25) +
  theme_minimal()


gfs25we <- data_nestline %>% ggplot(aes(x = nest, y = fs25we, color = Species)) +
  geom_point(size = 2) +
  scale_color_manual(values = c("Loggerhead" = "#004C97", "Green" = "#40A829")) +
  xlab("Nest") + 
  ylab("Difference (°)") + 
  ggtitle("Foreshore Slope", subtitle = "25E:25W") +
  ylim(min=-4, max=4) +
  theme_minimal()

  
  gfs50we <- data_nestline %>% ggplot(aes(x = nest, y = fs50we, color = Species)) +
  geom_point(size = 2) +
  scale_color_manual(values = c("Loggerhead" = "#004C97", "Green" = "#40A829")) +
  xlab("Nest") + 
  ylab("Difference (°)") + 
  ggtitle("Foreshore Slope", subtitle = "50E:50W") +
  ylim(min=-4, max=4) +
  theme_minimal()

  
  gfs100we <- data_nestline %>% ggplot(aes(x = nest, y = fs100we, color = Species)) +
  geom_point(size = 2) +
  scale_color_manual(values = c("Loggerhead" = "#004C97", "Green" = "#40A829")) +
  xlab("Nest") + 
  ylab("Difference (°)") + 
  ggtitle("Foreshore Slope", subtitle = "100E:100W") +
  ylim(min=-4, max=4) +
  theme_minimal()

 
  gbs25we <- data_nestline %>% ggplot(aes(x = nest, y = bs25we, color = Species)) +
  geom_point(size = 2) +
  scale_color_manual(values = c("Loggerhead" = "#004C97", "Green" = "#40A829")) +
  xlab("Nest") + 
  ylab("Difference (°)") + 
  ggtitle("Beach Slope", subtitle = "25E:25W") +
  ylim(min=-2, max=1.5) +
  theme_minimal()

  
  gbs50we <- data_nestline %>% ggplot(aes(x = nest, y = bs50we, color = Species)) +
  geom_point(size = 2) +
  scale_color_manual(values = c("Loggerhead" = "#004C97", "Green" = "#40A829")) +
  xlab("Nest") + 
  ylab("Difference (°)") + 
  ggtitle("Beach Slope", subtitle = "50E:50W") +
  ylim(min=-2, max=1.5) +
  theme_minimal()

  
  gbs100we <- data_nestline %>% ggplot(aes(x = nest, y = bs100we, color = Species)) +
  geom_point(size = 2) +
  scale_color_manual(values = c("Loggerhead" = "#004C97", "Green" = "#40A829")) +
  xlab("Nest") + 
  ylab("Difference (°)") + 
  ggtitle("Beach Slope", subtitle = "100E:100W") +
  ylim(min=-2, max=1.5) +
  theme_minimal()

  
  gbw25we <- data_nestline %>% ggplot(aes(x = nest, y = bw25we, color = Species)) +
  geom_point(size = 2) +
  scale_color_manual(values = c("Loggerhead" = "#004C97", "Green" = "#40A829")) +
  xlab("Nest") + 
  ylab("Difference (m)") + 
  ggtitle("Beach Width", subtitle = "25E:25W") +
  ylim(min=-15, max=13) +
  theme_minimal()

  
  gbw50we <- data_nestline %>% ggplot(aes(x = nest, y = bw50we, color = Species)) +
  geom_point(size = 2) +
  scale_color_manual(values = c("Loggerhead" = "#004C97", "Green" = "#40A829")) +
  xlab("Nest") + 
  ylab("Difference (m)") + 
  ggtitle("Beach Width", subtitle = "50E:50W") +
  ylim(min=-15, max=13) +
  theme_minimal()

  
  gbw100we <- data_nestline %>% ggplot(aes(x = nest, y = bw100we, color = Species)) +
  geom_point(size = 2) +
  scale_color_manual(values = c("Loggerhead" = "#004C97", "Green" = "#40A829")) +
  xlab("Nest") + 
  ylab("Difference (m)") + 
  ggtitle("Beach Width", subtitle = "100E:100W") +
  ylim(min=-15, max=13) +
  theme_minimal()

  
  gfh25we <- data_nestline %>% ggplot(aes(x = nest, y = fh25we, color = Species)) +
  geom_point(size = 2) +
  scale_color_manual(values = c("Loggerhead" = "#004C97", "Green" = "#40A829")) +
  xlab("Nest") + 
  ylab("Difference (m)") + 
  ggtitle("Foredune Height", subtitle = "25E:25W") +
  ylim(min=-1.5, max=1) +
  theme_minimal()

  
  gfh50we <- data_nestline %>% ggplot(aes(x = nest, y = fh50we, color = Species)) +
  geom_point(size = 2) +
  scale_color_manual(values = c("Loggerhead" = "#004C97", "Green" = "#40A829")) +
  xlab("Nest") + 
  ylab("Difference (m)") + 
  ggtitle("Foredune Height", subtitle = "50E:50W") +
  ylim(min=-1.5, max=1) +
  theme_minimal()

  
  gfh100we <- data_nestline %>% ggplot(aes(x = nest, y = fh100we, color = Species)) +
  geom_point(size = 2) +
  scale_color_manual(values = c("Loggerhead" = "#004C97", "Green" = "#40A829")) +
  xlab("Nest") + 
  ylab("Difference (m)") + 
  ggtitle("Foredune Height", subtitle = "100E:100W") +
  ylim(min=-1.5, max=1) +
  theme_minimal()

mgfsn <- ggarrange(gfsn25w, gfsn25e, gfsn50w, gfsn50e, gfsn100w, gfsn100e, ncol = 2,nrow = 3)
annotate_figure(mgfsn, top = text_grob("Foreshore Slope Difference with Nestline (Degrees)", color = "black", face = "bold", size = 20))

mgbsn <- ggarrange(gbsn25w, gbsn25e, gbsn50w, gbsn50e, gbsn100w, gbsn100e, ncol = 2,nrow = 3)
annotate_figure(mgbsn, top = text_grob("Beach Slope Difference with Nestline (Degrees)", color = "black", face = "bold", size = 20))

mgbwn <- ggarrange(gbwn25w, gbwn25e, gbwn50w, gbwn50e, gbwn100w, gbwn100e, ncol = 2,nrow = 3)
annotate_figure(mgbwn, top = text_grob("Beach Width Difference with Nestline (m)", color = "black", face = "bold", size = 20))

mgfhn <- ggarrange(gfhn25w, gfhn25e, gfhn50w, gfhn50e, gfhn100w, gfhn100e, ncol = 2,nrow = 3)
annotate_figure(mgfhn, top = text_grob("Foredune Height Difference with Nestline (m)", color = "black", face = "bold", size = 20))

mgwe1 <- ggarrange(gfs25we, gbs25we, gfs50we, gbs50we, gfs100we, gbs100we, ncol = 2,nrow = 3)
annotate_figure(mgwe1, top = text_grob("Foreshore Slope and Beach Slope Difference Between E and W (Degrees)", color = "black", face = "bold", size = 14))

mgwe2 <- ggarrange(gbw25we, gfh25we, gbw50we, gfh50we, gbw100we, gfh100we, ncol = 2, nrow = 3)
annotate_figure(mgwe2, top = text_grob("Beach Width and Foredune Height Difference Between E and W (M)", color = "black", face = "bold", size = 14))

# QQ Plots to Assess Normality

qqfsn25w <- ggplot(data_nestline, aes(sample = fsn25w)) +
  stat_qq(size=3) +
  stat_qq_line() +
  theme_minimal() +
  xlab("Theoretical") +
  ylab("Sample") +
  ggtitle("25w") +
  theme(text = element_text(size=16))


qqfsn25e <- ggplot(data_nestline, aes(sample = fsn25e)) +
  stat_qq(size=3) +
  stat_qq_line() +
  theme_minimal() +
  xlab("Theoretical") +
  ylab("Sample") +
  ggtitle("25e") +
  theme(text = element_text(size=16))


qqfsn50w <- ggplot(data_nestline, aes(sample = fsn50w)) +
  stat_qq(size=3) +
  stat_qq_line() +
  theme_minimal() +
  xlab("Theoretical") +
  ylab("Sample") +
  ggtitle("50w") +
  theme(text = element_text(size=16))


qqfsn50e <- ggplot(data_nestline, aes(sample = fsn50e)) +
  stat_qq(size=3) +
  stat_qq_line() +
  theme_minimal() +
  xlab("Theoretical") +
  ylab("Sample") +
  ggtitle("50e") +
  theme(text = element_text(size=16))


qqfsn100w <- ggplot(data_nestline, aes(sample = fsn100w)) +
  stat_qq(size=3) +
  stat_qq_line() +
  theme_minimal() +
  xlab("Theoretical") +
  ylab("Sample") +
  ggtitle("100w") +
  theme(text = element_text(size=16))


qqfsn100e <- ggplot(data_nestline, aes(sample = fsn100e)) +
  stat_qq(size=3) +
  stat_qq_line() +
  theme_minimal() +
  xlab("Theoretical") +
  ylab("Sample") +
  ggtitle("100e") +
  theme(text = element_text(size=16))


qqbsn25w <- ggplot(data_nestline, aes(sample = bsn25w)) +
  stat_qq(size=3) +
  stat_qq_line() +
  theme_minimal() +
  xlab("Theoretical") +
  ylab("Sample") +
  ggtitle("25w") +
  theme(text = element_text(size=16))


qqbsn25e <- ggplot(data_nestline, aes(sample = bsn25e)) +
  stat_qq(size=3) +
  stat_qq_line() +
  theme_minimal() +
  xlab("Theoretical") +
  ylab("Sample") +
  ggtitle("25e") +
  theme(text = element_text(size=16))


qqbsn50w <- ggplot(data_nestline, aes(sample = bsn50w)) +
  stat_qq(size=3) +
  stat_qq_line() +
  theme_minimal() +
  xlab("Theoretical") +
  ylab("Sample") +
  ggtitle("50w") +
  theme(text = element_text(size=16))


qqbsn50e <- ggplot(data_nestline, aes(sample = bsn50e)) +
  stat_qq(size=3) +
  stat_qq_line() +
  theme_minimal() +
  xlab("Theoretical") +
  ylab("Sample") +
  ggtitle("50e") +
  theme(text = element_text(size=16))


qqbsn100w <- ggplot(data_nestline, aes(sample = bsn100w)) +
  stat_qq(size=3) +
  stat_qq_line() +
  theme_minimal() +
  xlab("Theoretical") +
  ylab("Sample") +
  ggtitle("100w") +
  theme(text = element_text(size=16))


qqbsn100e <- ggplot(data_nestline, aes(sample = bsn100e)) +
  stat_qq(size=3) +
  stat_qq_line() +
  theme_minimal() +
  xlab("Theoretical") +
  ylab("Sample") +
  ggtitle("100e") +
  theme(text = element_text(size=16))


qqbwn25w <- ggplot(data_nestline, aes(sample = bwn25w)) +
  stat_qq(size=3) +
  stat_qq_line() +
  theme_minimal() +
  xlab("Theoretical") +
  ylab("Sample") +
  ggtitle("25w") +
  theme(text = element_text(size=16))


qqbwn25e <- ggplot(data_nestline, aes(sample = bwn25e)) +
  stat_qq(size=3) +
  stat_qq_line() +
  theme_minimal() +
  xlab("Theoretical") +
  ylab("Sample") +
  ggtitle("25e") +
  theme(text = element_text(size=16))


qqbwn50w <- ggplot(data_nestline, aes(sample = bwn50w)) +
  stat_qq(size=3) +
  stat_qq_line() +
  theme_minimal() +
  xlab("Theoretical") +
  ylab("Sample") +
  ggtitle("50w") +
  theme(text = element_text(size=16))


qqbwn50e <- ggplot(data_nestline, aes(sample = bwn50e)) +
  stat_qq(size=3) +
  stat_qq_line() +
  theme_minimal() +
  xlab("Theoretical") +
  ylab("Sample") +
  ggtitle("50e") +
  theme(text = element_text(size=16))


qqbwn100w <- ggplot(data_nestline, aes(sample = bwn100w)) +
  stat_qq(size=3) +
  stat_qq_line() +
  theme_minimal() +
  xlab("Theoretical") +
  ylab("Sample") +
  ggtitle("100w") +
  theme(text = element_text(size=16))


qqbwn100e <- ggplot(data_nestline, aes(sample = bwn100e)) +
  stat_qq(size=3) +
  stat_qq_line() +
  theme_minimal() +
  xlab("Theoretical") +
  ylab("Sample") +
  ggtitle("100e") +
  theme(text = element_text(size=16))


qqfhn25w <- ggplot(data_nestline, aes(sample = fhn25w)) +
  stat_qq(size=3) +
  stat_qq_line() +
  theme_minimal() +
  xlab("Theoretical") +
  ylab("Sample") +
  ggtitle("25w") +
  theme(text = element_text(size=16))


qqfhn25e <- ggplot(data_nestline, aes(sample = fhn25e)) +
  stat_qq(size=3) +
  stat_qq_line() +
  theme_minimal() +
  xlab("Theoretical") +
  ylab("Sample") +
  ggtitle("25e") +
  theme(text = element_text(size=16))


qqfhn50w <- ggplot(data_nestline, aes(sample = fhn50w)) +
  stat_qq(size=3) +
  stat_qq_line() +
  theme_minimal() +
  xlab("Theoretical") +
  ylab("Sample") +
  ggtitle("50w") +
  theme(text = element_text(size=16))


qqfhn50e <- ggplot(data_nestline, aes(sample = fhn50e)) +
  stat_qq(size=3) +
  stat_qq_line() +
  theme_minimal() +
  xlab("Theoretical") +
  ylab("Sample") +
  ggtitle("50e") +
  theme(text = element_text(size=16))


qqfhn100w <- ggplot(data_nestline, aes(sample = fhn100w)) +
  stat_qq(size=3) +
  stat_qq_line() +
  theme_minimal() +
  xlab("Theoretical") +
  ylab("Sample") +
  ggtitle("100w") +
  theme(text = element_text(size=16))


qqfhn100e <- ggplot(data_nestline, aes(sample = fhn100e)) +
  stat_qq(size=3) +
  stat_qq_line() +
  theme_minimal() +
  xlab("Theoretical") +
  ylab("Sample") +
  ggtitle("100e") +
  theme(text = element_text(size=16))

qqfs25we <- ggplot(data_nestline, aes(sample = fs25we)) +
  stat_qq(size=3) +
  stat_qq_line() +
  theme_minimal() +
  xlab("Theoretical") +
  ylab("Sample") +
  ggtitle("Foreshore Slope",subtitle = "25W:25E") +
  theme(text = element_text(size=8))


qqfs50we <- ggplot(data_nestline, aes(sample = fs50we)) +
  stat_qq(size=3) +
  stat_qq_line() +
  theme_minimal() +
  xlab("Theoretical") +
  ylab("Sample") +
  ggtitle("Foreshore Slope",subtitle = "50W:50E") +
  theme(text = element_text(size=8))


qqfs100we <- ggplot(data_nestline, aes(sample = fs100we)) +
  stat_qq(size=3) +
  stat_qq_line() +
  theme_minimal() +
  xlab("Theoretical") +
  ylab("Sample") +
  ggtitle("Foreshore Slope",subtitle = "100W:100E") +
  theme(text = element_text(size=8))


qqbs25we <- ggplot(data_nestline, aes(sample = bs25we)) +
  stat_qq(size=3) +
  stat_qq_line() +
  theme_minimal() +
  xlab("Theoretical") +
  ylab("Sample") +
  ggtitle("Beach Slope",subtitle = "25W:25E") +
  theme(text = element_text(size=8))


qqbs50we <- ggplot(data_nestline, aes(sample = bs50we)) +
  stat_qq(size=3) +
  stat_qq_line() +
  theme_minimal() +
  xlab("Theoretical") +
  ylab("Sample") +
  ggtitle("Beach Slope",subtitle = "50W:50E") +
  theme(text = element_text(size=8))


qqbs100we <- ggplot(data_nestline, aes(sample = bs100we)) +
  stat_qq(size=3) +
  stat_qq_line() +
  theme_minimal() +
  xlab("Theoretical") +
  ylab("Sample") +
  ggtitle("Beach Slope",subtitle = "100W:100E") +
  theme(text = element_text(size=8))


qqbw25we <- ggplot(data_nestline, aes(sample = bw25we)) +
  stat_qq(size=3) +
  stat_qq_line() +
  theme_minimal() +
  xlab("Theoretical") +
  ylab("Sample") +
  ggtitle("Beach Width",subtitle = "25W:25E") +
  theme(text = element_text(size=8))


qqbw50we <- ggplot(data_nestline, aes(sample = bw50we)) +
  stat_qq(size=3) +
  stat_qq_line() +
  theme_minimal() +
  xlab("Theoretical") +
  ylab("Sample") +
  ggtitle("Beach Width",subtitle = "50W:50E") +
  theme(text = element_text(size=8))


qqbw100we <- ggplot(data_nestline, aes(sample = bw100we)) +
  stat_qq(size=3) +
  stat_qq_line() +
  theme_minimal() +
  xlab("Theoretical") +
  ylab("Sample") +
  ggtitle("Beach Width",subtitle = "100W:100E") +
  theme(text = element_text(size=8))


qqfh25we <- ggplot(data_nestline, aes(sample = fh25we)) +
  stat_qq(size=3) +
  stat_qq_line() +
  theme_minimal() +
  xlab("Theoretical") +
  ylab("Sample") +
  ggtitle("Foredune Height",subtitle = "25W:25E") +
  theme(text = element_text(size=8))


qqfh50we <- ggplot(data_nestline, aes(sample = fh50we)) +
  stat_qq(size=3) +
  stat_qq_line() +
  theme_minimal() +
  xlab("Theoretical") +
  ylab("Sample") +
  ggtitle("Foredune Height",subtitle = "50W:50E") +
  theme(text = element_text(size=8))


qqfh100we <- ggplot(data_nestline, aes(sample = fh100we)) +
  stat_qq(size=3) +
  stat_qq_line() +
  theme_minimal() +
  xlab("Theoretical") +
  ylab("Sample") +
  ggtitle("Foredune Height",subtitle = "100W:100E") +
  theme(text = element_text(size=8))


mfsn <- ggarrange(qqfsn25w, qqfsn25e, qqfsn50w, qqfsn50e, qqfsn100w, qqfsn100e, ncol = 3,nrow = 2)
annotate_figure(mfsn, top = text_grob("Foreshore Slope Difference with Nestline", color = "black", face = "bold", size = 20))

mbsn <- ggarrange(qqbsn25w, qqbsn25e, qqbsn50w, qqbsn50e, qqbsn100w, qqbsn100e, ncol = 3,nrow = 2)
annotate_figure(mbsn, top = text_grob("Beach Slope Difference with Nestline", color = "black", face = "bold", size = 20))

mbwn <- ggarrange(qqbwn25w, qqbwn25e, qqbwn50w, qqbwn50e, qqbwn100w, qqbwn100e, ncol = 3,nrow = 2)
annotate_figure(mfsn, top = text_grob("Beach Width Difference with Nestline", color = "black", face = "bold", size = 20))

mfhn <- ggarrange(qqfhn25w, qqfhn25e, qqfhn50w, qqfhn50e, qqfhn100w, qqfhn100e, ncol = 3,nrow = 2)
annotate_figure(mfsn, top = text_grob("Foredune Height Difference with Nestline", color = "black", face = "bold", size = 20))

mwe <- ggarrange(qqfs25we, qqbs25we, qqbw25we, qqfh25we, qqfs50we, qqbs50we, qqbw50we, qqfh50we, qqfs100we, qqbs100we, qqbw100we, qqfh100we, ncol = 4,nrow = 3)
annotate_figure(mwe, top = text_grob("All Variables Difference Between E and W", color = "black", face = "bold", size = 20))



# Differences between nestline and other locations

#foreshore slope difference between nestline and other locations
t.test(data_nestline$foreshore_slope, data_25w$foreshore_slope, paired = TRUE, alternative = "two", conf.level = 0.9)

t.test(data_nestline$foreshore_slope, data_25e$foreshore_slope, paired = TRUE, alternative = "two", conf.level = 0.9)

t.test(data_nestline$foreshore_slope, data_50w$foreshore_slope, paired = TRUE, alternative = "two", conf.level = 0.9)

t.test(data_nestline$foreshore_slope, data_50e$foreshore_slope, paired = TRUE, alternative = "two", conf.level = 0.9)

t.test(data_nestline$foreshore_slope, data_100w$foreshore_slope, paired = TRUE, alternative = "two", conf.level = 0.9)

t.test(data_nestline$foreshore_slope, data_100e$foreshore_slope, paired = TRUE, alternative = "two", conf.level = 0.9)

#beach slope difference between nestline and other locations
t.test(data_nestline$beach_slope, data_25w$beach_slope, paired = TRUE, alternative = "two", conf.level = 0.9)

t.test(data_nestline$beach_slope, data_25e$beach_slope, paired = TRUE, alternative = "two", conf.level = 0.9)

t.test(data_nestline$beach_slope, data_50w$beach_slope, paired = TRUE, alternative = "two", conf.level = 0.9)

t.test(data_nestline$beach_slope, data_50e$beach_slope, paired = TRUE, alternative = "two", conf.level = 0.9)

t.test(data_nestline$beach_slope, data_100w$beach_slope, paired = TRUE, alternative = "two", conf.level = 0.9)

t.test(data_nestline$beach_slope, data_100e$beach_slope, paired = TRUE, alternative = "two", conf.level = 0.9)

#beach width difference between nestline and other locations
t.test(data_nestline$beach_width, data_25w$beach_width, paired = TRUE, alternative = "two", conf.level = 0.9)

t.test(data_nestline$beach_width, data_25e$beach_width, paired = TRUE, alternative = "two", conf.level = 0.9)

t.test(data_nestline$beach_width, data_50w$beach_width, paired = TRUE, alternative = "two", conf.level = 0.9)

t.test(data_nestline$beach_width, data_50e$beach_width, paired = TRUE, alternative = "two", conf.level = 0.9)

t.test(data_nestline$beach_width, data_100w$beach_width, paired = TRUE, alternative = "two", conf.level = 0.9)

t.test(data_nestline$beach_width, data_100e$beach_width, paired = TRUE, alternative = "two", conf.level = 0.9)

#foredune height difference between nestline and other locations
t.test(data_nestline$foredune_height, data_25w$foredune_height, paired = TRUE, alternative = "two", conf.level = 0.9)

t.test(data_nestline$foredune_height, data_25e$foredune_height, paired = TRUE, alternative = "two", conf.level = 0.9)

t.test(data_nestline$foredune_height, data_50w$foredune_height, paired = TRUE, alternative = "two", conf.level = 0.9)

t.test(data_nestline$foredune_height, data_50e$foredune_height, paired = TRUE, alternative = "two", conf.level = 0.9)

t.test(data_nestline$foredune_height, data_100w$foredune_height, paired = TRUE, alternative = "two", conf.level = 0.9)

t.test(data_nestline$foredune_height, data_100e$foredune_height, paired = TRUE, alternative = "two", conf.level = 0.9)


# Differences between 25E and 25W, 50E and 50W, and 100E and 100W

#foreshore slope difference between 25 E and 25W, etc.
t.test(data_25w$foreshore_slope, data_25e$foreshore_slope, paired = TRUE, alternative = "two", conf.level = 0.9)

t.test(data_50e$foreshore_slope, data_50w$foreshore_slope, paired = TRUE, alternative = "two", conf.level = 0.9)

t.test(data_100e$foreshore_slope, data_100w$foreshore_slope, paired = TRUE, alternative = "two", conf.level = 0.9)

#beach slope difference between 25 E and 25W, etc.
t.test(data_25w$beach_slope, data_25e$beach_slope, paired = TRUE, alternative = "two", conf.level = 0.9)

t.test(data_50e$beach_slope, data_50w$beach_slope, paired = TRUE, alternative = "two", conf.level = 0.9)

t.test(data_100e$beach_slope, data_100w$beach_slope, paired = TRUE, alternative = "two", conf.level = 0.9)

#beach width difference between 25 E and 25W, etc.
t.test(data_25w$beach_width, data_25e$beach_width, paired = TRUE, alternative = "two", conf.level = 0.9)

t.test(data_50e$beach_width, data_50w$beach_width, paired = TRUE, alternative = "two", conf.level = 0.9)

t.test(data_100e$beach_width, data_100w$beach_width, paired = TRUE, alternative = "two", conf.level = 0.9)

#foredune height difference between 25 E and 25W, etc.
t.test(data_25w$foredune_height, data_25e$foredune_height, paired = TRUE, alternative = "two", conf.level = 0.9)

t.test(data_50e$foredune_height, data_50w$foredune_height, paired = TRUE, alternative = "two", conf.level = 0.9)

t.test(data_100e$foredune_height, data_100w$foredune_height, paired = TRUE, alternative = "two", conf.level = 0.9)
```

